Quality-of-Content (QoC)-Based Wireless Video Transmissions: A Joint Source Coding and APP-FEC Rate Allocation Scheme for Human Detections in Mobile Surveillance Networks

### 2015-08-09 draft.tex
1. Modified the bib 2. Added the first simulation results.

\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{Video Resolutions and Human Densities}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{1.9cm}!{\vrule width 2pt}p{2.7cm}|p{2.7cm}|}
\hline
\textbf{Rate Allocation Scheme} & \textbf{Source Coding Rate} & \textbf{APP-FEC Rate} \\ \noalign{\hrule height 2pt}
\textbf{Proposed} & Adaptive, QoC-driven & Adaptive, QoC-driven \\ \hline
\textbf{MSE} & Adaptive, MSE-driven & Adaptive, determined by pre-determined targets \\ \hline 
\textbf{Equal ($0.5$)} & Fixed, $50$\% of total available throughput  & Fixed, $50$\% of total available throughput \\ \hline
\textbf{Equal ($0.8$)} &Fixed, $80$\% of total available throughput &Fixed, $20$\% of total available throughput \\
\hline
\end{tabular}
\end{center}
\label{Table: schemes}
%\vspace{-.1in}
\end{table}

>>>>

\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{Video Resolutions and Human Densities}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{1.9cm}!{\vrule width 2pt}p{2.7cm}|p{2.7cm}|}
\hline
\textbf{Rate Allocation Scheme} & \textbf{Source Coding Rate} & \textbf{APP-FEC Rate} \\ \noalign{\hrule height 2pt}
\textbf{Proposed} & Adaptive, QoC-driven & Adaptive, QoC-driven \\ \hline
\textbf{MSE} & Adaptive, MSE-driven & Adaptive, driven by pre-determined targets \\ \hline 
\textbf{Equal ($0.5$)} & Fixed, $50$\% of total available throughput  & Fixed, $50$\% of total available throughput \\ \hline
\textbf{Equal ($0.8$)} &Fixed, $80$\% of total available throughput &Fixed, $20$\% of total available throughput \\
\hline
\end{tabular}
\end{center}
\label{Table: schemes}
%\vspace{-.1in}
\end{table}

\begin{figure}[t]
\centering{\epsfig{file=Fig/dataRateAdaptation_2800_1.eps,width=3.6in}}
\caption{Instantaneous source coding data rate (Kbps) of each video under total transmission data rate: 2800 Kbps. Packet loss rate of each video is $1\%$.}\label{fig:inst_dataRate_2800_1}
\end{figure}
\begin{figure}[t]
\centering{\includegraphics[width=3.5 in]{Fig/humanDensityChange_1.pdf}}
\caption{The sample frames of the video sequence ``LOEWENPLATZ" of different human densities. Left: a sample video frame of the $10^{\text{th}}$ GoP; Right: a sample video frame of the $12^{\text{th}}$ GoP.}
\label{fig:humanDensityChange_1}
\end{figure}

In the first simulation scenario, the packet loss rates of all the testing video sequences are set as $1\%$. When the packet loss rates are fair among all the videos, the only cause of data rate allocations is either content or distortion for the proposed content-driven scheme or the traditional distortion-driven scheme respectively. Figure \ref{fig:inst_dataRate_2800_1} shows the instantaneous source coding data rate (Kbps) of each video when the total transmission data rate constraint is 2800 Kbps. For the proposed content-driven scheme, more source coding data rates are allocated to the videos with higher human densities. Note that the rate allocation algorithm of the proposed content-driven scheme depends on the detected human densities of the previous GoP. For instance, the data rate allocated to the video sequence ``LOEWENPLATZ" significantly increases from the $11^\text{th}$ GoP to the $13^\text{th}$ GoP. This is because of the increasing of detected human densities as illustrated in Fig. \ref{fig:humanDensityChange_1}. For the distortion-driven scheme, more data rate is allocated to the video sequence with more image details (i.e., UW 1).

Figure \ref{fig:avg_dataRate_1} shows the average source coding data rate (Kbps) of each video sequence under different transmission data rate constraints. It is obvious that more source coding data rates are allocated to all the video sequences. For the proposed content-driven scheme, the data increasing rates (slopes) of the videos with higher human densities are higher than those with less human densities. For the distortion-driven scheme, the data increasing rates do not depend on the human densities. As shown in Fig. \ref{fig:avg_fec_redundancy_rate_1}, more data rates are allocated to APP-FEC redundancies for better protections of the transmitted videos when the overall transmission data rate constraints are increasing. Similar as the source coding rate allocation, the proposed content-driven scheme allocates more FEC protections to the videos with more human densities, while the distortion-driven scheme does not. The APP-FEC rate of an $\left(n,k\right)$ code is defined as the $k/n$. The average APP-FEC rates of each video under different total transmission data rate constraints are plotted in Fig. \ref{fig:avg_fec_rate_1}. Most of the FEC rates are slightly increasing when more data rate is available for transmissions since the increasing rates of source coding rates are higher than that of the APP-FEC redundancies. However, for the proposed content-driven scheme, the APP-FEC rate of the video sequence ``UW 1" is decreasing, which is due to the fact that few source coding data rate is allocated even when more total data rate is available (shown in Fig. \ref{fig:avg_dataRate_1}) because of the few human densities of the video scene.

\begin{figure}[t]
\centering{\epsfig{file=Fig/averagSourceCodingRate_1.eps,width=3.6in}}
\caption{Average source coding data rate (Kbps) of each video under different transmission data rate constraints. Packet loss rate of each video is $1\%$.}\label{fig:avg_dataRate_1}
\end{figure}

\begin{figure}[t]
\centering{\epsfig{file=Fig/averageFECRedundancyRate_1.eps,width=3.6in}}
\caption{Average data rate (Kbps) of APP-FEC redundancy under different transmission data rate constraints. Packet loss rate of each video is $1\%$.}\label{fig:avg_fec_redundancy_rate_1}
\end{figure}

\begin{figure}[t]
\centering{\epsfig{file=Fig/averageFECRate_1.eps,width=3.6in}}
\caption{Average APP-FEC rate of each video under different transmission data rate constraints. Packet loss rate of each video is $1\%$.}\label{fig:avg_fec_rate_1}
\end{figure}

The average true-positive detection probability and the average false-alarm probability for each rate allocation scheme are plotted in Fig. \ref{fig:true_positive_1} and Fig. \ref{fig:false_alarm_1} respectively. Obviously, the proposed content-driven scheme more effectively allocates both of the source coding rate and the APP-FEC rate and can achive higher true-positive detection probability and less false-alarms.

\begin{figure}[t]
\centering{\epsfig{file=Fig/truePositiveProb_dataConstraint_1.eps,width=3.6in}}
\caption{Average true-positive detection probability under different transmission data rate constraints. Packet loss rate of each video is $1\%$.}\label{fig:true_positive_1}
\end{figure}

\begin{figure}[t]
\centering{\epsfig{file=Fig/falseAlarm_dataConstraint_1.eps,width=3.6in}}
\caption{Average false-alarm probability under different transmission data rate constraints. Packet loss rate of each video is $1\%$.}\label{fig:false_alarm_1}
\end{figure}

In the second simulation scenario, the packet loss rates of the video sequences ``UW 1" and ``LOEWENPLATZ" are set as $3\%$ while that of the other two are set as $1\%$.
